
\documentclass[10pt]{article}
\usepackage[a4paper, margin=0.9cm]{geometry}

\usepackage[familydefault,light]{Chivo}
\usepackage{hyperref}

\pagenumbering{gobble}

\usepackage{xcolor}
\definecolor{dark}{RGB}{30,90,150}
\definecolor{light}{RGB}{220, 240, 255}
% \definecolor{dark}{gray}{0}
\definecolor{mid}{gray}{0.5}
% \definecolor{light}{gray}{0.9}


\newcommand{\bold}[1]{\textbf{\textcolor{dark}{#1}}}

\newcommand{\sect}[1]{{\LARGE\bold{#1}}\vspace{0.2em}\\}

\newcommand{\xx}[2]{{\large\bold{#1}}\\{#2}\vspace{0.5em}}

\newcommand{\zz}[3]{{\large\bold{#1}} \hfill {\small \colorbox{light}{\texttt{#3}}}\\{#2}\vspace{0.5em}}


\newcommand{\li}{\textcolor{mid}{|}}

\begin{document}

\begin{center}
{\color{dark}\Huge Luke\textbf{Storry}}
\hspace{0.1em}

{\large \href{mailto:Luke@LukeStorry.co.uk}{Luke@LukeStorry.co.uk}  $|$  07805 925658} 

Bristol Computer Science MEng Student with a love of the outdoors.\\
\vspace{-0.5em}
{\color{dark}\hrulefill}
\end{center}




% % %  C O L U M N  O N E  % % %

\begin{minipage}[t]{0.33\textwidth}
\raggedright

1.29  The Hawthorns\\Woodland Road\\Bristol\\BS81UQ

\vspace{0.5em}
%\href{https:lukestorry.co.uk}{\bold{LukeStorry}.co.uk} \\
\href{https://github.com/lukestorry}{github.com/\bold{\textcolor{dark}{lukestorry}}} \\
%\href{https://www.linkedin.com/in/lukestorry}{LinkedIn.com/in/\bold{lukestorry}} \\
%\href{https://instagram.com/lukestorry}{Instagram.com/\bold{lukestorry}}\\

\vspace{0.5em}
\sect{Other Work}
\xx{UoB Chief Senior Resident}
{Supervising a team of Senior Residents as part of the University's ResiLife pastoral welfare system. Developing and maintaining communities within halls, running events, and providing vital support for students in need.
% Part of the university's pastoral and welfare teams, developing and maintaining communal life, running a variety of events throughout the year, as well as providing support for students in need.
}

\xx{SWA Head Of Media}
{Lead a team of eight event photographers, videographers and article writers, whilst coordinating with the logistics and marketing teams, to advertise and promote the Student Windsurfing Association.
%a non-profit set up to coordinate and develop student windsurfing across the UK.
% Working with event photographers, videographers and article writers to cultivate loads of juicy media for students to read and scroll through whilst they’re procrastinating their studies, spreading the word about how awesome windsurfing is to get more people out on the water.
}

\xx{CS Outreach Coordinator}
{Worked with University staff to enhance the department's outreach program, both on open days and visits to local schools. 
Designed \& ran workshops for a variety of ages, with the aim of inspiring the next generation of engineers and software developers.}

\xx{Chief Windsurfing Instructor}
{Led and managed a team of 17 instructors providing tuition to over 100 beginners and 50 intermediates at the SWA Aussie Kiss Festival.}

% \xx{Windsurfing Instructor}
% {Summer seasons, June-September\\
% \bold{2015} - MW San Lucianu, Corsica\\
% \bold{2016} - MW Lemnos Hotel, Greece\\
% \bold{2017} - Windsurf Vassiliki, Greece\\
% Worked as part of close-knit beach teams at watersports centers.\\
% Variety of roles: teaching adults and children, boat-carrying, equipment repair, and safety-boat driving.}

\vspace{0.4em}
\sect{Hobbies}

\xx{Climbing}
{Boulder indoors \& out multiple times a week, and starting to develop my trad-climbing skills.}

\xx{Windsurfing}
{Won first place in the intermediate fleet at BUCS Nationals 2017, alongside multiple years of experience as an instructor and coach.}

\xx{Hiking}
{I have a deep-seated love of mountains and coastal walks, and have completed multiple week-long hikes along the SW Coast path.}

\xx{Kayaking}
{Regularly surf-kayak, gained 2nd place in Canoe Freestyle at the UK's National Student Rodeo event 2017.}
% and have completed BCU 4* Whitewater Leader training.}

\end{minipage} 
\hfill
%
%
%
% % %  C O L U M N  T W O  % %
%
\begin{minipage}[t]{0.65\textwidth}
\raggedright


\sect{Education}
\zz{University of Bristol}
{MEng Computer Science \small{(Expecting \bold{2.1})}}{2014-2019}

\zz{Exeter College}
{International Baccalaureate \bold{38} \\  
\hspace{1em} {\small - HL: English, Physics, Chemistry, SL: Maths, German, Psychology}\\
A-Level Mathematics \bold{A*}, AS Further Mathematics \bold{A}, AS Computing \bold{A}}
{2011-2014}


\vspace{0.4em}
\sect{Relevant Work Experience}

\zz{Swanbarton - Software Engineer}
{Successfully delivered a variety of energy storage and trading products, as a member of the research \& development team at an energy-management consultancy.

Given a mixture of legacy code and new designs, my modular, full-stack and fully-tested Python code solved problems ranging from cloud-based optimization through to low-level control of industrial batteries.

I also helped transition the software team over to an agile "scrum-ban" approach, by implementing a Jira-based workflow that greatly increased productivity whilst requiring less oversight from management.}
{Python\li PyUnit\li Jira\li Docker\li Archi}




\vspace{0.35em}
\sect{University Programming experience}

\zz{Games Project}
{Worked in a team of 6 to develop a complex networked multiplayer game.\\
Designed an efficient algorithm for the procedural-generation of the layout of a city and surrounding map, and built various other aspects of the game.}
{Unity\li C\#\li Scrum Agile\li git}

\zz{\href{https://lukestorry.co.uk/simple_read/}{Simple\_Read}}
{Winning entry to CSS Accessibility Hackathon.\\
Chrome extension that analyses the reading age of web articles, then simplifies the text to a reading age that is on average 22\% lower.}{Javascript\li JSON\li HTML\li CSS\li Chrome APIs}

\zz{Web Technologies}
{Developed a simple web store, with a range of windsurfing products dynamically loaded from a database, a  user accounts system, a cart stored in cookies, a search feature, and a design-your-own-sail app.}
{Pug\li Node.js\li Express\li SQL\li XHTML\li CSS\li Heroku}

% \zz{Interactive Devices}
% {Designed and built a interactive devices, including hardware and software prototypes, then used quantitative and qualitative techniques to evaluate user experiences.}
% {}

% \zz{Cloud Computing}
% {Created an efficiently-scaling cloud application.}
% {Docker\li Kubernetes\li AWS\li MongoDB}

% \zz{Applied Deep Learning}
% {Replicated state-of-the-art learning performance, using a deep architecture on a publicly available dataset.}
% {TensorFlow\li Python}

\zz{Systems Security}
{Executed and developed defences against a range of security vulnerabilities.}
{Vagrant\li C\li GDB\li SQL\li Bash\li Assembly\li Netwox}

\zz{Machine Learning}
{Used statistical analysis, modelling and inference for the classification and de-noising of complex datasets, and wrote two scientific reports on the use of those techniques.}
{Python\li NumPy\li SciPy\li Matplotlib}

\zz{High Performance Computing}
{Designed, implemented and analyzed high performance parallel versions of matrix-operation algorithms on the Blue Crystal supercomputer cluster.\\
Serial speedups of 26x, and 150x on 16 parallel cores.}
{C\li OpenMP\li BASH}

\zz{Software Product Engineering}
{Five-member team prototyped new media storage and retrieval systems for atBristol's exhibits, whilst streamlining booking and entry to the museum.}{Firebase\li Node.js\li HTML5\li Android}

\zz{Human-Computer Interaction}
{Planned, built, and conducted a psychological experiment, comparing the input speeds of touchscreen vs mouse.}{Python\li Tkinter\li SPSS\li LaTeX}

\zz{Image Processing and Computer Vision}
{Applied a variety of Computer Vision algorithms and methods to detect dartboards in noisy images, with an F1-score of 125x the stock VJ method.}
{Python\li OpenCV\li LaTeX}

% \zz{Artificial Intelligence with Logic Programming}
% {Utilized the automated inference features of Prolog to implement a variety of AI and natural-language-processing algorithms}{Prolog}

% \zz{Concurrent Computing}
% {Produced an efficient Game Of Life program for the XMOS xCore-200 board.}{Python\li PyUnit\li C\li XC\li CSP}

% \zz{Computational Neuroscience}
% {Simulated models of neurons, networks, and cortical areas.}{Python\li Julia}

% \zz{Language Engineering}
% {Created tools to parse, verify and compile a simple custom language.}{Haskell}

% \zz{Programming \& Algorithms}
% {Constructed a variety of programs to explore different coding paradigms, culminating in a fully-tested board game simulation with integrated AI and networking.}{Java\li Ant\li AWT\li Javascript}
% \\




\vspace{0.5em}



% \zz{\href{https://lukestorry.co.uk/JuliaSets/}{Julia Sets}}{Visualization of Julia Set fractals on the complex plane.}{C\li Python}

% \zz{FlappyBird on Scratch}{Designed workshop for use in schools, teaching KS2 children how to code by developing their own customized version of the then-viral FlappyBird game.}{Scratch\li LaTeX}

% \zz{Code-a-Clock}{Online worksheet for use in demo lab sessions at University Open Days.}{Java\li Processing\li GitHub Pages\li Jekyll}


\end{minipage} 
\end{document}
